\tool{}: Specification- and Syntax-based Automated Testing Linguistic Capabilities of NLP Models

### 2023-01-11 paper/fse23/related.tex
related work

\MyPara{Text Generation}
%
Different data augmentation approaches have been proposed for text generation. One of methods in this category is easy data augmentation (EDA)~\cite{weizou2019eda}. It uses simple operations such as synonym replacement and random swap. Coulombe~\cite{coulombe2018textaugapi} implements rule-based transformations using regular expressions for text transformations such as insertion of spelling mistakes, data alterations, entity names, and abbreviations. Mixup interpolation, which was introduced in computer vision category, was implemented in text domain~\cite{hongyu2019dataaugmixup}. Learning-based language models has been used to generate text data for multiple tasks~\cite{qizhe2019unsupdataaug, ateret2019lambda}. While these approaches focus on obtaining synthetic training data, not testing NLP model over \lcs,
% they are not able to be used for the capability testing of the NLP model, 
our work generates text data for testing NLP model over \lcs.

>>>>

\MyPara{Text Generation}
%
Different data augmentation approaches have been proposed for text
generation. One of methods in this category is easy data augmentation
(EDA)~\cite{weizou2019eda}. It uses simple operations such as synonym
replacement and random swap. Coulombe~\cite{coulombe2018textaugapi}
implements rule-based transformations using regular expressions for
text transformations such as insertion of spelling mistakes, data
alterations, entity names, and abbreviations. Mixup interpolation,
which was introduced in computer vision category, was implemented in
text domain~\cite{hongyu2019dataaugmixup}. Learning-based language
models has been used to generate text data for multiple
tasks~\cite{qizhe2019unsupdataaug, ateret2019lambda}. While these
approaches focus on obtaining synthetic training data, not testing NLP
model over \lcs,
% they are not able to be used for the capability testing of the NLP model, 
our work generates text data for testing NLP model over \lcs.  In
addition, adversarial text generation methods has been used for
attacking NLP
model~\cite{morris2020textattack,zang2020sememepso,alzantot2018genadvexp,linyang2020bertattack}. Morris \textit{\etal}~\cite{morris2020textattack}
transform input text by leveraging existing methods such as insertion,
deletion and swap of word/character within the similarity-based
constraints. Zang \textit{\etal}~\cite{zang2020sememepso} finds
sememe-based synonyms and generates adversarial examples by the word
substitution. Alzantot \textit{\etal}~\cite{alzantot2018genadvexp}
substitutes word in an input text with its neighboring words in
embedding space that fools an NLP
model. Linyang \textit{\etal}~\cite{linyang2020bertattack} generates
word substitutes with BERT predicted words for attacking an NLP
model. Also, Grammar-based text generation has been also
introduced~\cite{udeshi2019ogma,soremekun2020astraea,maIJCAI2020mtnlp}.
Ogma~\cite{udeshi2019ogma} and Astraea~\cite{soremekun2020astraea}
leverages predefined grammar, and search adversarial examples by
replacing word in an input text with another one that conforms to same
production rule in the grammar until the replacement leads to error in
the model. Ma \textit{\etal}~\cite{maIJCAI2020mtnlp} applies a simple
expansion that inserts an adjective word before noun besides to
replacement of analogy word found in embedding space. Our work
generates text data does not only rely on the word substitution, but
also changes diverse structures from the input text. In addition, we
generates text conforming to same context of input text and its
corresponding \lc by investigating its semantic and syntax.
